### 2018-12-17 README.Rmd
rename data objects

data(aw_stl_asthma, package = "areal")
asthma <- aw_stl_asthma

data(aw_stl_race, package = "areal")
race <- aw_stl_race

data(aw_stl_wards, package = "areal")
wards <- aw_stl_wards
```

@@

* `aw_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
* `aw_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
* `aw_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
* `aw_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).

>>>>

data(ar_stl_asthma, package = "areal")
asthma <- aw_stl_asthma

data(ar_stl_race, package = "areal")
race <- aw_stl_race

data(ar_stl_wards, package = "areal")
wards <- aw_stl_wards
```

@@

* `ar_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
* `ar_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
* `ar_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
* `ar_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).
